
\section{Spectrometer}
\label{sec:spectrometer}

There are two main goals the spectrometer is expected to fulfill. The first is
to measure the mean energy and energy spread of the beam, as it is this
measurement that determines the success of the AWAKE project, i.e.  whether or
not the electrons were accelerated up to the desired
\SI{1.3}{\giga\electronvolt}, which would demonstrate the use of large EM
gradients of \SI{\sim1}{\giga\volt\per\meter}. The second goal it to measure the
quality of the beam which can quantitatively be described by it's emittance
which is defined in Section~\ref{sec:emittance}.


\subsection{Design Overview}

A C-shaped dipole magnet with a maximum setting of \SI{650}{\ampere} is placed
downstream of the plasma cell in order to separate the electron and proton
beams, as well as measure the energy and energy spread of the beam by deflecting
electrons onto a \SI{65}{\milli\meter} high by \SI{1}{\meter} wide scintillator
screen. The amount by which each electron is deflected, and hence it's
horizontal position on the screen, can be directly related to it's energy.  To
improve the ratio of the electron beam signal to the background noise, a
quadrupole doublet is placed upstream of the dipole.  This will focus electrons
that are at a certain energy onto the screen and under or over--focus electrons
that are at different energies. This will result in a vertical spread of
electrons that are tightly focused at the horizontal position on the screen
pertaining to the mean energy of the beam, gradually becoming less focused and
more spread out further from this horizontal position. The emittance of the beam
cannot directly be measured since it is a measure of both the beam size and beam
divergence. However from the shape of the incident beam on the screen and an
understanding of the effects of the quadrupole and the dipole, a function can be
derived which calculates the initial emittance of the beam.

Due to large amounts of background radiation in the main tunnel, the intensified
CCD camera (Andor iStar 340T) will be situated \SI{17}{\meter} from the screen
in an adjacent tunnel. Light from the screen will be reflected onto the camera
using a series of mirrors~\cite{deacon2016qjq} and the goals of the spectrometer
will be achieved by analysing the signal received by this camera.

